Natural sources of vagueness and their implications

### 2017-05-11 book_chapter/paper.tex
section on rationality

Finally, we might be interested in a notion of meaning of language as an abstraction over their users and its use.
We might not care about individual agents' behavior and beliefs as much as we care about the meaning of words, expressions and sentences.
The questions to address then are probably: what explanatory purpose is a notion of meaning of an abstracted language to play?; if both agents' rational behavior and rational beliefs are plausibly fuzzy, why should a concept of supervening meaning be crisp?; what can be explained only by a notion of meaning that is not vague?
\mf{I leave this paragraph in for you to read and ponder, but would recommend to leave it out entirely}

>>>>

% Finally, we might be interested in a notion of meaning of language as an abstraction over their users and its use.
% We might not care about individual agents' behavior and beliefs as much as we care about the meaning of words, expressions and sentences.
% The questions to address then are probably: what explanatory purpose is a notion of meaning of an abstracted language to play?; if both agents' rational behavior and rational beliefs are plausibly fuzzy, why should a concept of supervening meaning be crisp?; what can be explained only by a notion of meaning that is not vague?
% \mf{I leave this paragraph in for you to read and ponder, but would recommend to leave it out entirely}
